\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS4_Patel.tex}
\author{shreyapatel }
\date{February 2018}

\begin{document}

\maketitle

\section{Introduction}

I think it would be interesting to find tweets about the hackathon community. I've used the Twitter API to scrape tweets before, and it's pretty interesting. I've also seen a project related to the Harry Potter series before. This is more a text analytics project but still interesting! http://uc-r.github.io/sentiment_analysis\\


R Exercise B\\
6.\\
    \indent 4. class(df1) is data.frame class(df) is SparkDataFrame

    \\
    \indent 5a. 1          5.1  setosa
2          4.9  setosa
3          4.7  setosa
4          4.6  setosa
5          5.0  setosa
6          5.4  setosa

    \\
    \indent 5b.unable to find an inherited method for function ‘select’ for signature ‘"data.frame", "Column"’ Because the data frame was saved to df, and the iris data set itself was saved to df1.

    \\
    \indent 6a.
    Sepal_Length Sepal_Width Petal_Length Petal_Width    Species
1          5.8         4.0          1.2         0.2     setosa
2          5.7         4.4          1.5         0.4     setosa
3          5.7         3.8          1.7         0.3     setosa
4          7.0         3.2          4.7         1.4 versicolor
5          6.4         3.2          4.5         1.5 versicolor
6          6.9         3.1          4.9         1.5 versicolor

    \\
    \indent 6b.  unable to find an inherited method for function ‘filter’ for signature ‘"data.frame", "Column"’ Because the data frame was saved to df, and the iris data set itself was saved to df1.

    \\



\end{document}
